API design for machine learning software: experiences from the scikit-learn project

### 2013-08-13 paper.tex
Cite sofia-ml

Other existing machine learning packages
such as SofiaML\footnote{\url{http://code.google.com/p/sofia-ml/}}
and Vowpal~Wabbit\footnote{\url{http://hunch.net/$\sim$vw/}}
are intended to be used as command-line tools
(and sometimes do not offer any type of API).
While these packages have the advantage
that their users are not tied to a particular programming language,
the users will find that they still need programming to process input/output,
and will do so in a variety of languages.
By contrast, \sklearn allows users to implement that entire workflow
in a single program, written in a single language,
and developed in a single working environment.
This also makes it easier for researchers and developers
to exchange and collaborate on software, as dependencies and setup are kept to a
minimum.

@@

While part of the \sklearn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.
The power, and extensibility of the \sklearn API is evidenced
by the large and growing user-base, its use to solve real
problems across a wide array of fields,
as well as the appearance of third-party packages
that follow the \sklearn conventions. Examples of such packages include
\textit{astroML}\footnote{\url{http://astroml.org/}}
\citep{vanderplas2012astroML}, a package providing
machine learning tools for astronomers, and
\textit{wiseRF}\footnote{\url{http://wise.io}}, a commercial random forest
implementation. The source code of
the recently-proposed sparse multiclass
algorithm of \citet{mblondel-mlj2013}, released as
part of the
\textit{lightning}\footnote{\url{https://github.com/mblondel/lightning}}
package, also follows the \sklearn conventions.
To maximize ease of use, we encourage more researchers
to follow these conventions when releasing their software.

>>>>

Other existing machine learning packages
such as SofiaML\footnote{\url{https://code.google.com/p/sofia-ml}}~\citep{sculley2009large}
and Vowpal~Wabbit\footnote{\url{http://hunch.net/$\sim$vw}}
are intended to be used as command-line tools
(and sometimes do not offer any type of API).
While these packages have the advantage
that their users are not tied to a particular programming language,
the users will find that they still need programming to process input/output,
and will do so in a variety of languages.
By contrast, \sklearn allows users to implement that entire workflow
in a single program, written in a single language,
and developed in a single working environment.
This also makes it easier for researchers and developers
to exchange and collaborate on software, as dependencies and setup are kept to a
minimum.

@@

While part of the \sklearn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.
The power, and extensibility of the \sklearn API is evidenced
by the large and growing user-base, its use to solve real
problems across a wide array of fields,
as well as the appearance of third-party packages
that follow the \sklearn conventions. Examples of such packages include
\textit{astroML}\footnote{\url{http://astroml.org}}
\citep{vanderplas2012astroML}, a package providing
machine learning tools for astronomers, and
\textit{wiseRF}\footnote{\url{http://wise.io}}, a commercial random forest
implementation. The source code of
the recently-proposed sparse multiclass
algorithm of \citet{mblondel-mlj2013}, released as
part of the
\textit{lightning}\footnote{\url{https://github.com/mblondel/lightning}}
package, also follows the \sklearn conventions.
To maximize ease of use, we encourage more researchers
to follow these conventions when releasing their software.
